---
title: "Alcohol vs Seat choice"
author: "Zanya Davenport"
date: "Summer 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
Based off the boxplot the median of people who sit in the back as I see it is higher than both the third quantile of people who sit in the front and the third quantile those who sit in the middle.
  
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The third quantile of the front is 2 and the the third quantile of the middle is 3. The median of the back is 4 so in this case the median of the back is higher than the third quantile of both the front and middle.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

After running the Inferential test we find that the probability of the people in the front and middle consuming the same amount of alcohol as the people in the back being 0.000116. Therefore there is a significant difference between the 3.

```{r}
plot(TukeyHSD(model1))
```

When looking at the model we see that the middle compared to the back does not have 0 in their confidence interval. The same is true when you compare the front and the back. This also indicates that their is no statistical difference between the front and the middle. The back is diffrent from everybody else. 

## Conclusions


