---
title: "Alcohol vs Seat choice"
author: "Zanya Davenport"
date: "Summer 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
Based off the boxplot the median of people who sit in the back as I see it is higher than both the third quantile of people who sit in the front and the third quantile those who sit in the middle.
  
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The third quantile of the front is 2 and the the third quantile of the middle is 3. The median of the back is 4 so in this case the median of the back is higher than the third quantile of both the front and middle.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

After running the Inferential test we find that the probability of the people in the front and middle consuming the same amount of alcohol as the people in the back being 0.000116. Therefore there is a significant difference between the 3.

```{r}
plot(TukeyHSD(model1))
```

When looking at the model we see that the middle compared to the back does not have 0 in their confidence interval. The same is true when you compare the front and the back. This also indicates that their is no statistical difference between the front and the middle. The back is different from everybody else. 

## Conclusions

When going through the process with more than two variables there are more steps that we have to go through which can complicate the process. In this assignment we used ggplot to create our boxplot which showed us the median of how man drinks were consumed per section. Then we ran a Numerical summary of the information so that we could get exact numbers and see how big the difference was. After this we ran the Inferential test to get the probability of these three sections consuming the same amount of alcohol which was 0.000116. We then used a comparison model that showed us how significant the difference between each section was. I have came to the conclusion that there is a significant difference between how much alcohol the three sections consumed. 


